StreamReduce: Processing Data Streams\\and Avoiding Work

### 2012-05-10 paper/paper.tex
Tweak Evaluation section

\begin{figure}
\includegraphics[width=\linewidth]{long-tail-ranks.png}
\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-tailed distribution.}
\label{fig:wordDist}
\end{figure}

@@

@@

@@

\begin{table}
\begin{tabularx}{\linewidth}{|c|c|X|}
\hline
Task kill rate & Work level & Average execution time [minutes] \\ \hline
0.0 & 1.0 & 11:35.5 \\ \hline
0.0 & 0.4 & 10:33.8 \\ \hline
0.0 & 0.8 & 10:30.8 \\ \hline
0.2 & 0.4 & 08:25.8 \\ \hline
0.2 & 0.8 & 08:37.8 \\ \hline
0.4 & 0.4 & 06:54.0 \\ \hline
0.4 & 0.8 & 06:28.2 \\ \hline
0.6 & 0.4 & 04:14.7 \\ \hline
0.6 & 0.8 & 04:13.7 \\ \hline
0.8 & 0.4 & 02:33.3 \\ \hline
0.8 & 0.8 & 02:15.0 \\ \hline
\end{tabularx}
\caption{Impact of task kill rate and work level on job execution time.}
\label{table:runtime}
\end{table}

@@

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{long-tail-ranks.png}
\caption{The frequencies of words in the Wikipedia Featured Articles corpus have a long-tailed distribution. This graph has had stopwords~\cite{stopwords} filtered out of it.}
\label{fig:wordDist}
\end{figure}

@@

\subsubsection{Recall}
Recall in the tail of the distribution is most dependent on the work level of the word count job.
Anything less than perfect computation of a datum leaves out words with a frequency of one.
Figure~\ref{fig:recall} shows how recall improves as the work level increases. Task killing has
the same effect on recall as using low fidelity computation routines, so recall decreases as
the task kill rate does. Task killing dominates the impact of work level on recall as demonstrated
by the two lines converging in Figure~\ref{fig:recall}.

Poor recall statistics are acceptable because I am running a top-k job that focuses
on good precision in the top~100. Because I use a weighted $F$-score, the poor recall's impact
on measured accuracy is mitigated.

\begin{figure}
\includegraphics[width=\linewidth]{recall.png}
\caption{Fraction of the bottom~10000 results returned in the result set by the word count job.}
\label{fig:recall}
\end{figure}

@@

The average reduction in $F_{0.5}$-score caused by reducing the work level form 0.8 to 0.4 is
$0.231$ with a standard deviation of $0.025$. I performed four additional experiments with the
work level set to $0.8$ and $0.4$ with the task kill rate set to $0.1$ and $0.7$. These experiments were
not included in generating Figure~\ref{fig:fscore}. The average reduction in $F_{0.5}$-score between
work level $0.8$ and $0.4$ in these experiments is $0.230$ with a standard deviation of
$0.056$. These numbers show that a $0.4$ reduction in the work level leads to approximately a
$0.23$ reduction in $F_{0.5}$-score.

@@

\begin{table}
\begin{tabularx}{\linewidth}{|X|X|X|X|}
\hline
Task kill rate & Work level & Average execution time [s] & $F_{0.5}$-score \\ \hline\hline
0.0 & 1.0 & 696 & 1.000 \\ \hline
0.0 & 0.8 & 631 & 0.939 \\ \hline
0.0 & 0.4 & 634 & 0.725 \\ \hline\hline
0.2 & 1.0 & 531 & 0.933 \\ \hline
0.2 & 0.8 & 518 & 0.890 \\ \hline
0.2 & 0.4 & 506 & 0.627 \\ \hline\hline
0.4 & 1.0 & 393 & 0.829 \\ \hline
0.4 & 0.8 & 388 & 0.797 \\ \hline
0.4 & 0.4 & 414 & 0.552 \\ \hline\hline
0.6 & 1.0 & 292 & 0.774 \\ \hline
0.6 & 0.8 & 254 & 0.690 \\ \hline
0.6 & 0.4 & 255 & 0.453 \\ \hline\hline
0.8 & 1.0 & 144 & 0.541 \\ \hline
0.8 & 0.8 & 135 & 0.489 \\ \hline
0.8 & 0.4 & 153 & 0.290 \\ \hline
\end{tabularx}
\caption{Impact of task kill rate and work level on job execution time and $F_{0.5}$-score.}
\label{table:runtime}
\end{table}

@@

\subsection{Speed vs. Accuracy Tradeoffs}
\begin{center}
\begin{table*}
  \begin{tabularx}{\linewidth}{|lr|lr|lr|}
    \hline
    \multicolumn{2}{|X|}{Work level = 1.0 and task kill rate = 0.0} &
    \multicolumn{2}{|X|}{Work level = 0.8 and task kill rate = 0.4} &
    \multicolumn{2}{|X|}{Work level = 0.4 and task kill rate = 0.8} \\ \hline
    33225 & title & 21184 & title & 5982 & title \\ \hline
    29356 & web & 18398 & web & 4689 & web \\ \hline
    23095 & book & 13591 & journal & 4225 & journal \\ \hline
    21821 & journal & 13429 & book & 3629 & year \\ \hline
    20124 & year & 12770 & publisher & 3617 & publisher \\ \hline
    19786 & publisher & 12550 & url & 3444 & url \\ \hline
    19478 & url & 12220 & year & 3410 & book \\ \hline
    17360 & news & 11511 & news & 3273 & news \\ \hline
    16685 & accessdate & 11082 & united & 2968 & accessdate \\ \hline
    16401 & united & 10691 & accessdate & 2582 & world \\ \hline
  \end{tabularx}
  \caption{Example top~10 results and their frequencies from several different job configurations. The top~10 do not change much one changes the paramters to make the job less accurate.}
  \label{table:top10}
\end{table*}
\end{center}

Because the word distribution is so skewed toward the head, there is a great potential to
speed up the calculation by killing tasks without having to sacrifice too much accuracy.
Additionally, Table~\ref{table:runtime} shows that the most significant time savings comes
from increasing the kill rate and keeping the work level high yields about a~20 percentage point
increase in $F_{0.5}$-score.

The best combination of parameters is a high work level and as high a task kill rate one can
manage with respect to one's target distortion level.
